### 2020-12-30 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/introduction.tex
intro 8

Section 2 contains the details of our methodology, where we aim to present a reproducible theoretical framework.

Section 3 provides the experimental setup

Section 4 presents the results

Section \ref{relatedwork} presents the related work

Section 6 concludes the paper.

>>>>

\begin{itemize}
\item[$-$] Section 2 contains the details of our methodology, where we aim to present a reproducible theoretical framework.
\item[$-$] Section 3 provides the experimental setup
\item[$-$] Section 4 presents the results
\item[$-$] Section \ref{relatedwork} presents the related work
\item[$-$] Section 6 concludes the paper.
\end{itemize}
